week getbackontrack

### 2024-11-04 plotting1.Rmd
weekbacktrackchange

```
## wave 2 - soc
```{r}
testsoc_w2 <- igraph::graph_from_adjacency_matrix(
  testsoc$nets[2,,], #take the second wave 
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL
  )

>>>>

## wave 2 - soc
```{r}
testsoc_w2 <- igraph::graph_from_adjacency_matrix(
  testsoc$nets[2,,], #take the second wave 
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL
  )

### 2024-11-04 weekbacktrack.Rmd
weekbacktrackchange

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |

@@

|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |

@@

>>>>

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |

@@

|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |

@@

|                                                                                               | [university]                                               |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
